---
title: "R Notebook"
output: html_notebook
---

#Assertive Programming

know what assertive programming is and why it is useful
Be able to use asserr and stopifnot to write assertions

  Maintain Reproducibility/Replicability
  
```{r}
library(tidyverse)
library(CodeClanData)
library(assertr)
weather_one <- read_csv("/Users/markfojas/CodeClan/de13_classnotes/week_02/day_4/2_assertive_programming/data/delhi_weather_one.csv")
weather_two <- read_csv("/Users/markfojas/CodeClan/de13_classnotes/week_02/day_4/2_assertive_programming/data/delhi_weather_two.csv")
```


```{r}


weather_report <- function(weather){
 weather %>% 
    
    verify(humidity >=0 & humidity <=100)
    verify(wind_speed >= 0 & wind_speed <= 108)
    verify(temp >= -35 & temp <=55) %>%
   
    
  # Our average temperature, humidity and wind speed 
  weather_means <- weather %>%
  summarise(
    mean_temp = mean(temp),
    mean_humidity = mean(humidity),
    mean_windspeed = mean(wind_speed)
  )

# Show hot and humid days
hot_and_humid <- 
weather %>% 
  filter(temp > 20) %>% 
  filter(humidity > 55)

return(list(weather_means, hot_and_humid))
}


weather_report(weather_one)
```
  
```{r}
weather2 <- read_csv("/Users/markfojas/CodeClan/de13_classnotes/week_02/day_4/2_assertive_programming/data/delhi_weather_two.csv")
```

  Task - 5 minutes
  Add an apropriate assertion for humidity, Hint: Humidity is a percentage.
  
```{r}
weather_report(weather_two)
```
  Change the order of assertions so we check humidity before temperature and see how the error message differs and see how the error message differs.
 
 output: 
  Error in isTRUE(attr(data, "assertr_data_defective")) : 
object 'humidity' not found
3.
isTRUE(attr(data, "assertr_data_defective"))
2.
verify(humidity >= 0 & humidity <= 100)
1.
weather_report(weather_two)


```{r}

#check for missing data


  weather_report <- function(weather){
  
  stopifnot(
      nrow(weather) > 15,
      ncol(weather) == 4,
      drop_na(weather) == weather
    )
    
  weather %>% 
    verify(humidity >= 0 & humidity <= 100) %>% 
    verify(wind_speed >= 0 & wind_speed <=108) %>% 
    verify(temp >= -35 & temp <= 55)
    
  
  # Our average temperature, humidity and wind speed 
  weather_means <- weather %>% 
    summarise(
      mean_temp = mean(temp),
      mean_humidity = mean(humidity),
      mean_windspeed = mean(wind_speed)
    )

  # Show hot and humid days
  hot_and_humid <- weather %>% 
    filter(temp > 20) %>% 
    filter(humidity > 55)
  
  return(list(weather_means, hot_and_humid))
}
```
```{r}
 # select(date, temp) %>% 
  weather_report(weather_one)
```


  