---
title: "R Notebook"
output: html_notebook
---
```{r}
library(prob)
library(gtools)
library(tidyverse)
library(here)
```
```{r}
#loading data
titanic_df <- read_csv(here("data/titanic.csv"))
```
A data set detailing the survival or death of passengers and crew members on the RMS Titanic is given in the data folder for this homework - use this data and not the built-in Titanic dataset in R.

Some time after the disaster a journalist wrote that crew members were more likely to have survived the sinking than passengers. This was disputed by a descendant of one of the surviving crew members, who suggested that the opposite was true, i.e. passengers were more likely to have survived than crew.

Question
Calculate the conditional probabilities prob(survived∣crew)
 and prob(survived∣passenger)
 to settle this dispute.

```{r}
names(titanic_df)
```
```{r}
glimpse(titanic_df)
head(titanic_df)
tail(titanic_df, 100)
```
```{r}
# getting intial count and set(s)
titanic_df %>% 
count(class)
summarise()
```

```{r}
#cleaning data, adding columns
titanic_modif <- titanic_df %>% 
  select(class, survived ) %>% 
  mutate(crew = str_detect(class,"crew|staff")) %>% 
  mutate(passengers = str_detect(class, "1st|2nd|3rd")) #could also do a negate of previous mutation, but want to do a different method to verify numbers
  
```


```{r}
#checking data
titanic_modif %>% 
  count(crew)

titanic_modif %>% #checking the other end of count to verify numbers-- seems to match
  count(passengers)
```


```{r}
#applying equations
#add columns of passenger and crew together to get subset

  
  

```





Have a look at the distinct values of the class variable, this will tell you whether each individual was a passenger (1st, 2nd or 3rd class) or a member of the crew (treat restaurant staff as crew)

titanic_modif %>% 





Question 1.
If I roll a six-sided dice once, what is the probability of getting a number less than 5?


Question 2.
How many outcomes are there in the sample space of an experiment in which we toss three dice?



Question 3.
In an experiment where we roll four dice:

how many outcomes are in the event where the total of the four dice equals 5
, 6
 or 7
)?
what is the probability of this event?
what assumptions do we apply in answering part ii?
 Hint


Question 4.
Five chairs are placed in a row in a room, along with five people of differing height. The people sit down randomly on the chairs. What is the probability that they sit in order of decreasing height, left to right?

 Hint

