---
title: "R Notebook"
output: html_notebook
---
___MVP Supply Chain Project___
# loading libraries
```{r}
library(tidyverse)
library(janitor)
library(here)
library(dplyr)
library(readxl)
library(CodeClanData) #realizing my chosen dataset was far less interesting from an app perspective, I decided to move on
```

```{r}
#reading supply chain dataset obtained from Kaggle, and cleaning
supplychain_order <- read_excel(here::here("data/Supply chain logisitcs problem.xlsx"), sheet = "OrderList")

supplychain_order_clean <- supplychain_order %>% 
  clean_names()
```
```{r}
#analyzing dimensions and names
dim(supplychain_order_clean) 
names(supplychain_order_clean)
head(supplychain_order_clean)

```
```{r}
#removing extraneous columns
supply_chain <- supplychain_order_clean %>% 
  group_by(origin_port, destination_port, customer, unit_quantity, weight, carrier, order_date )
```


```{r}
ggplot(supply_chain) +
  aes(x = order_date, y = unit_quantity, group = origin_port) +
  geom_bar() 
  
  
```
-A few hours into this dataset, getting charts and graphs that looked like a straight line no matter how I rotated axes, I looked at my notes, looked at the chart, then realized to my horror: This dataset only spans ONE date. This underscores the importance of looking at ALL data. This would 


/* The other 6 tables describe the restrictions imposed on the system.

some customers can only be serviced by a specific plant
plants and ports have to be physically connected.
plants can only handle specific items
Notes:

The terms "Warehouse" and "Plant" are used interchangeably, essentially a warehouse is a plant.
This is a (deterministic) optimization problem, there is only one order date since we are only looking at orders from one specific day and trying to assign them to routes/factories.
We have to ship all the orders to PORT09
The goal is to schedule routes while minimizing freight and warehousing costs. 


This dataset was taken from the Brunel University of London Website */




