```{r}
library(tsibbledata)
library(tsibble)
library(lubridate)
library(slider)
library(tidyverse)
```
Try to periodically check in - am I answering what is being asked? Do I truly understand what I’m being asked? Do I understand how the answer to these questions/analysis will be implemented and affect the business? Do I know who the end user of my analysis is? It’s ok if not but be sure to ask (specific) questions to the client to find out.



```{r}
nyc_bikes_df <- nyc_bikes #seems to already be a tibbble


glimpse(nyc_bikes_df)
index(nyc_bikes_df)
head(nyc_bikes)
tail(nyc_bikes)

#getting unique values for type, gender, subscriber

```
```{r}

distinct(nyc_bikes_df, type)
distinct(nyc_bikes_df, gender)
```


3 Task hints
You will probably want to use the data in column start_time to create date, month and year columns.
Summarising the data by aggregating hire counts by different measures of time (e.g. year, quarter, month, day) and then visualising the results is probably a good idea
When grouping time series data (tsibble), you need to use index_by instead of group_by

```{r}
#creating calendar and age columns
nyc_bikes_df <- nyc_bikes_df %>% 
  mutate(day = as_date(start_time),
         year = year(start_time),
         quarter = quarters(start_time),
         month = month(start_time),
         biker_age = (year(start_time) - birth_year),
         trip_duration = round(
           (
             ymd_hms(stop_time)) - (ymd_hms(start_time)
                                  ), digits = 1
           )
         ) 

```

```{r}
#quick stats, and bike user profile

        
median(nyc_bikes_df$biker_age)

nyc_bikes_df %>% 
  filter(gender == "Female") %>% 
  count()
 # column is numeric but still get need numeric data even after using na.rm=TRUE

nyc_bikes_df %>% 
  filter(gender == "Male") %>% 
  count()

nyc_bikes_df %>% 
  filter(gender == "Unknown") %>% 
  count()

nyc_bikes_df %>% 
  slice_min(biker_age)

nyc_bikes_df 
  
```

Average user is 35 and male



# transforming into tsibble

```{r}
bikes_data_tsibble <- as_tsibble(nyc_bikes_df, key = c(bike_id, start_station, end_station, gender, biker_age, year, quarter, month, day, trip_duration), index = start_time)
bikes_data_tsibble
```

```{r}
# Sanity check on tsibble
test_tibble <- nyc_bikes %>% 
  mutate(day = as_date(start_time)) %>% 
  index_by(day) %>% 
  as_tibble()
```

```{r}
#Visualizing
# possibly use facets to contrast gender/age/customer type over time in this limited data set-- may possibly incorporate larger datasets from client site but this is out of scope for now!

nyc_bikes_df%>% 
  filter(gender == c("Male","Female")) %>% 
ggplot() +
  aes(x = trip_duration, y = gender) +
  geom_point() 

  

  
  

```

```{r}
nyc_bikes_df%>% 
filter(gender == c("Male","Female")) %>% 
ggplot() +
  aes(day, color = gender) +
  geom_bar() 
  
```
```{r}

```


