---
title: "R Notebook"
output: html_notebook
---
# Regular Expressions


```{r}
og_string <- "We're going to replace some words"

str_sub(og_string, 1, 5) <- "I am"

og_string
```

This previous technique is not dynamic

Regex lets us define a search pattern

`stringr function(string, pattern, some_other_arguments)`

## Pattern Matching

- validating inputs (check postcodes are formatted correctly)
- finding substrings
- generally working with text data

```{r}
single_string <- "heinz beans"
a_vector_of_strings <- c(
  "first",
  "second",
  "third",
  "fourth",
  "fifth",
  "sixth",
  "seeeeeventh"
)
```

Let's start by looking for the letter "i"

```{r}
pattern <- "i"
str_detect(single_string, pattern)
str_detect(a_vector_of_strings, pattern)
str_detect(a_vector_of_strings, pattern, negate = TRUE)
```


### Matching multiple characters

```{r}
pattern <- "fir"
str_detect(single_string, pattern)
str_detect(a_vector_of_strings, pattern)
```
```{r}
pattern <- "[fir]"
str_detect(a_vector_of_strings, pattern)
```

Special Characters

"[a,b,c]" square brackets define a set
```{r}
pattern <- "e{3}"
str_detect(a_vector_of_strings, pattern)
```
We can define a range of characters wihin a set

```{r}
pattern <- "[a-e]"
str_detect(a_vector_of_strings, pattern)
```
```{r}
pattern <- "[a-z]"
str_detect(a_vector_of_strings, pattern)
```

By default regular expressions are case sensitive

{} - specify a minimum number of preceding characters to match


# can make them case insensitive
```{r}
pattern <- "(?i)[A-Z]"
str_detect(a_vector_of_strings, pattern)
```

Make a vector containing the following strings:

"We're having great fun learning about data analysis at CodeClan!"
"CodeClan is at 37 Castle Terrace in Edinburgh, ClockWise in Glasgow, and Wasps Academy in Inverness"
"Our cohort code starts with DE, DG or D"
"You get a great view of the castle or the national conservatoire from just outside CodeClan's door"
Write and test regular expressions which will match:

Any string mentioning CodeClan
Any string containing two consecutive capital letters
Any string not including the word "castle" or "Castle"

```{r}

fun_vector <- c("We're having great fun lerning about data analysis at CodeClan!", 
         "CodeClan is at 37 Castle Terrace in Edinburgh, ClockWise in Glasgow, and Wasps Academy in Inverness",
         "Our cohort code starts with DE, DG or D",
         "You get a great view of the castle or the national conservatoire from just outside CodeClan's door"
         )

pattern_codeclan <- "CodeClan"

str_detect(fun_vector, pattern_codeclan)


str_extract_all(fun_vector, "[A-B]{2}")

pattern <- "[Cc]astle")
str_detect(fun_vector, pattern, negate = TRUE)

```
str_detect(vector, "(?i)castle", negate = TRUE)

```{r}
vector_with_emails <- c(
  "This string has an_address@email.com in it", 
  "This one has user.name@company.co.uk", 
  "Now we've got other_person_123@server.net and my.name@runningoutofideas.com"
)

vector_with_emails
```

```{r}
pattern <- "[a-z]"
str_extract(vector_with_emails, pattern)
```

```{r}
pattern <- "[a-z]@"
str_extract(vector_with_emails, pattern)
```

"*" match __none__ or more of preceding expression

```{r}
pattern <- "[a-z]*@"
str_extract(vector_with_emails, pattern)
```

Another special character

"+" one or more

```{r}
pattern <- "[a-z]+@"
str_extract(vector_with_emails, pattern)
```

```{r}
pattern <- "[a-z0-9]+@[a-z]+"
str_extract(vector_with_emails, pattern)
```

pattern <- "[:alnum:]+@[:alnum:]+"
```{r}
pattern <- "[:alnum:]+@[:alnum:]+"
str_extract(vector_with_emails, pattern)
```
## Replacing parts of a string

```{r}
pattern <- "[:alnum:]+@[:alnum:]+"
str_replace_all(vector_with_emails, pattern, replacement = "REDACTED")
```

extract all the names





Task - 8 mins
"David's mobile number definitely isn't 07777777777."
"A landline might be 01010 123456."
"Jamie, John, Chris and David have been some of your instructors so far."
"I'm called your_name_here and I live in your_town_here."
```{r}
challenge <- c("David's mobile number definitely isn't 07777777777.", 
               "A landline might be 01010 123456.",
               "Jamie, John, Chris and David have been some of your instructors so far.",
               "I'm called your_name_here and I live in your_town_here.")

pattern <- "[A-Z][a-z]+"
str_extract_all(challenge, pattern)
```


extract the landline number
pattern <- [0-9]+
```{r}
pattern <- "[0-9]+"
str_extract_all(challenge, pattern)
```

```{r}


str_replace(challenge, )
```


Insert your name an where you live into the fourth string

## Other helpful

^     start of string
$     end of string
.     match all characters
-. 
\     literal
```{r}
str_extract(challenge, "^[A-Za-z]")
#grab the first letter



str_extract(challenge, "[:punct:]$")
#grab the last character
```
```{r}
str_extract(challenge, ".+[1]")
```

### Working with Tibbles
```{r}
student <- c("Abigail", "Bjorn", "Caitlin")
age <- c(25, 56, 40)
emails <- c("abigal12@company.co.uk", "bsmith@gmail.co.uk", "caitlin_1980")

student_info <- tibble(student, age, emails)

student_info %>% 
  filter(str_detect(student, "^[C|c]"))
```
```{r}
glimpse(student_info)
```

```{r}
valid_email <- "[a-z0-9_.]+@[a-z_.]+"
student_info %>% 
  mutate(valid = str_detect(emails, valid_email))
```

```{r}
student_info %>% 
  mutate(emails = str_replace(emails, valid_email, "REDACTED"))
```

