---
title: "R Notebook"
output: html_notebook
---
```{r}
library(tidyverse)
library(janitor)
```

1 MVP
1.1 Joins

Question 1

Read in all 4 credit card transaction datasets and clean column names.

```{r}
transactionbase <- read_csv("/Users/markfojas/CodeClan/codeclan_homework_MarkAntFojas/week2/Day1/data/TransactionBase.csv")
cardbase <- read_csv("/Users/markfojas/CodeClan/codeclan_homework_MarkAntFojas/week2/Day1/data/CardBase.csv")
customerbase <- read_csv("/Users/markfojas/CodeClan/codeclan_homework_MarkAntFojas/week2/Day1/data/CustomerBase.csv")
fraudbase <- read_csv("/Users/markfojas/CodeClan/codeclan_homework_MarkAntFojas/week2/Day1/data/FraudBase.csv")
```
```{r}
transactionbase
cardbase
customerbase
fraudbase
```



Question 2

Join the data containing card details and customer details by customer id, so that all records of card details and any matching records in customer details are kept. Before you run the code, think about how many rows you expect to see after joining.

```{r}
#We return only 500 records because we want to keep only those rose in x (customerbase), that match with y (cardbase). 
right_join(
  customerbase, 
  cardbase, 
  by = 'Cust_ID')
  
```

Question 3

Join the data containing fraud details with transaction details so all rows of both tables are kept. What does the resulting row number tell you?

```{r}
#to preserve ALL rows of both x and y you want full_join
full_join(transactionbase, 
          fraudbase, 
          by = 'Transaction_ID')
```

Question 4

Join the data containing card details with transaction details so rows from the first which have matching ones in the second are returned, but only return rows in the first table once. 
```{r}
#We want to left_join sorting by Card Number where x = cardbase, so that Card Number is the primary key. In the transactions details, Credit_Card_ID is not unique. We will also need to correspond the values of Credit_Card_ID to Card Number.


left_join(cardbase, 
          transactionbase, 
          by = c("Card_Number" = "Credit_Card_ID" ))

```


```{r}

```

1.2 tidyr
Question 5

Read in hat_observations and separate observation into two columns, hat_colour and hat_type.

```{r}
hat_observations <- read_csv("/Users/markfojas/CodeClan/codeclan_homework_MarkAntFojas/week2/Day1/data/hat_observations.csv")

glimpse(hat_observations)
head(hat_observations)

sep_observation <- hat_observations %>% 
  separate(observation, c("hat_color", "hat_type")), sep = "//.,"

sep_observation            )
```



Question 6

Unite day, month, and year columns into a column called date using a suitable separator. Then find the date where the most berets were observed.

```{r}
dated_observation <- sep_observation %>% 
unite('date', day, month, year, sep = "/")

dated_observation
```

```{r}
dated_observation %>% 
select(date, hat_type, observation_count)
                  

```


2 Extension
2.1 Joins
Question 1

Can you join all 4 datasets together so that you’re left with a dataset that looks like below with 109 rows and 12 columns?



2.2 tidyr
Question 2

Read in exam_scores and transform it into long format with two new columns exam_question and score. Then, using separate and select, remove superfluous information from the values in exam_question