---
title: "R Notebook"
output: html_notebook
---

Tidy Data Mini-Lab
Duration: 30 minutes

Now it’s your turn to practice the verbs on a new dataset. Complete the following task:

1 MVP
Task 1.
Load in the country_data.csv file and take a look at it. What needs changed in this to make it tidy? Which columns need made into long format, and which need spread to rows?
-years values need to be made longer.
-type needs to be spread into rows.
```{r}
country_data <- read_csv("/Users/markfojas/CodeClan/de13_classnotes/week_02/day_1/4_tidy_data_mini_lab/data/country_data.csv")


```



Task 2.
Do the appropriate pivoting of your columns using R

```{r}
country_longer <- country_data %>% 
  pivot_longer(cols = starts_with("Y"),
               names_to = "Year",
               values_to = "Year_Value",
               names_prefix = "Y")
country_longer

country_wider <- country_longer %>% 
    pivot_wider(names_from = "type",
                values_from = "Year_Value")

country_wider
```



Task 3.
Separate the country variable so you have the name in one column and the number in another.
```{r}
sep_country <- country_wider%>% 
  separate(country, into = c("country_code", "Nation"), sep = "\\. " )

```





Task 4.
Unite the code_letter and code_numb variables so that they are both in one column, with no spaces separating them. 

```{r}
unite_value <- sep_country%>% 
  unite ("Code", code_letter, code_numb, sep = "", remove = TRUE, na.rm = FALSE)
  

unite_value
```

