```{r}
#loading libraries
library(here)
library(infer)
library(janitor)
library(tidyverse)
```
```{r}
#loading data
ames <- read_csv(here("data/ames.csv")) %>% 
  clean_names()
```
```{r}
glimpse(ames)
```
task 2

Investigate the distribution of lot_area. Is the distribution roughly normal? If not, what problems do you find?
```{r}
ggplot(ames) +
  aes(x = lot_area) +
  geom_histogram(col = "white", fill = "steel blue", bins  = 40)
```
This is not a normal distribution, skewing right and is also centrally concentrated.


Task 3.
Compute and visualise a bootstrap sampling distribution for the mean(lot_area) of the sold houses.

```{r}
bootstrap_sample_dist <- ames %>%
  specify(response = lot_area) %>%
  generate(reps = 5000, type = "bootstrap") %>%
  calculate(stat = "mean")

bootstrap_sample_dist %>%
  visualise(col = "white", fill = "steel blue", bins = 30)
```

Task 4.
Use your bootstrap distribution to calculate a 95%
 CI for mean(lot_area), and visualise it on the distribution

```{r}
ci_95 <- bootstrap_sample_dist %>%
  get_ci(level = 0.95, type = "percentile")

ci_95

bootstrap_sample_dist %>% 
visualise(bins = 30) +
  shade_confidence_interval(endpoints = ci_95)
```

