---
title: "R Notebook"
output: html_notebook
---
___MVP Supply Chain Project___
# loading libraries
```{r}
library(tidyverse)
library(janitor)
library(here)
library(dplyr)
library(readxl)
```

```{r}
#reading supply chain dataset obtained from Kaggle, and cleaning
supplychain_order <- read_excel(here::here("data/Supply chain logisitcs problem.xlsx"))

supplychain_order_clean <- supplychain_order %>% 
  clean_names()
```
```{r}
#analyzing dimensions and names
dim(supplychain_order_clean) 
names(supplychain_order_clean)
head(supplychain_order_clean)

```
```{r}
#removing extraneous columns
supply_chain <- supplychain_order_clean %>% 
  group_by(origin_port, destination_port, customer, unit_quantity, weight, carrier, order_date)
```


```{r}
ggplot(supply_chain) +
  geom_point(
  aes(x = order_date, y = unit_quantity)) 
  
  
```

/* The other 6 tables describe the restrictions imposed on the system.

some customers can only be serviced by a specific plant
plants and ports have to be physically connected.
plants can only handle specific items
Notes:

The terms "Warehouse" and "Plant" are used interchangeably, essentially a warehouse is a plant.
This is a (deterministic) optimization problem, there is only one order date since we are only looking at orders from one specific day and trying to assign them to routes/factories.
We have to ship all the orders to PORT09
The goal is to schedule routes while minimizing freight and warehousing costs.
I am also just working on understanding the Dataset, maybe we can have a discussion in the comment section for clarifications.
Acknowledgements:

This dataset was taken from the Brunel University of London Website */