```{r}
#loading libraries
library(CodeClanData)
library(janitor)
library(tidyverse)
library(here)
```
```{r}
#loading and analyzing data
salaries <- read_csv(here("data/salaries.csv")) %>%
  clean_names()
glimpse(salaries)
```
1. Use select to see the beginning salary variable and the current salary variable.
```{r}

salaries %>%
  select(beginning_salary, current_salary)
```
2. Use filter to see the employees aged over 50, who have a salary over £20,000.

```{r}
over50_salaries <- salaries %>% 
  filter ("age" >= 50 & "current_salary" >= 20000)
```
3. Use arrange to order by the data so that the highest salaries are first.

```{r}
salaries %>%
  select(current_salary, age, everything()) %>% 
  arrange(desc(current_salary), .by_group = TRUE) 
```
4. Use mutate to make a new variables beginning_salary_pence and current_salary_pence. These should have the corresponding salaries in pence instead of pounds.

```{r}
salaries_in_pence <- salaries %>% 
mutate(beginning_salary_pence = beginning_salary * 100, current_salary_pence = current_salary * 100) %>% 
select(current_salary_pence, beginning_salary_pence)
```

5.Use summarise to find the maximum age and the minimum age

```{r}
salaries %>% 
summarise(min_age = min(age), max_age = max(age))
```

6. Find the minimum salary and the maximum salary
```{r}
salaries %>% 
summarise(min_salary = min(current_salary), max_salary = max(current_salary))
```

7. Find all the employees aged under 30.
```{r}
salaries %>% 
group_by(employment_category) %>% 
mutate(under_30 = (age < 30)) %>% 
summarise(under_30 = TRUE, employment_category) 
```
8. Order the data in terms of increasing educational level where ties are broken using age.

```{r}
salaries %>% 
arrange(educational_level, desc(age)) %>% #sorted age descending just to to see a tidy nest of brackets and remind myself that this was possible.
group_by(educational_level, age) %>% 
select(educational_level, age, employment_category) #added employment_category for my own assessment of data


```







