---
title: "R Notebook"
output: html_notebook
---

```{r}
library(dplyr)
library(janitor)
library(tidyverse)
library(CodeClanData)
```

```{r}
books_data <- read_csv("/Users/markfojas/CodeClan/codeclan_homework_MarkAntFojas/week1/weekend/books.csv")

glimpse(books_data)

```

#Curious to see how many rows have missing values

```{r}
nrow(books_data) - nrow(drop_na(books_data))

```

#I don't believe it! No missing data?! Let's try a different technique. Going to attempt an across function and sum missing data across all columns

```{r}

books_data %>%   
  summarise(across(fns= ~sum(is.na(.x))))
```

#I'm still skeptical that there are no missing values, but spent considerable time visually checking the data. I haven't gone through every single row IRL, but I'm moving forward with the idea that my coding doesn't contain serious logical errors or assumptions.

#Create a dataframe that selects for columns of interest to reduce processor useage. Initially isbn and isbn13 seems redundant. I want to check that all isbn entries have a corresponding isbn13 entry. The older pre 2007 isbns have 10 characters vs the modern isbn13 (13 character) standard. I want to determine na's for isbn and isbn13

```{r}
isbn_data <- books_data %>% 
  select(isbn,isbn13)


#summarise and categorize via columns any na's in all rows
#tidyverse::map(isbn_data, ~sum(is.na(.))) is also a valid technique. Have used three separate techniques! Q to ask on a tangent: purrr is a tidyverse package, but is it's own library?

#creating a dataframe for the work we've done using across
missing_books <- books_data %>%   
  summarise(across(fns= ~sum(is.na(.x))))

missing_books






  
```

#Conclusion: unless isbn is specifically needed, it can be a redundant identifier when making relations between columns. It can be dropped.

#Let's do something slightly more interesting. I want to summarise and mutate and maybe consolidate eng and eng-us, replacing both with value 'ENG'

#First, I'm going to select only the columns I find of interest and create a second df--- to clean things up in the resulting tibble

books_data

```{r}

```

