---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
```

Review of Day 2 Lab work


Other peoples code

whole_text %>% 
  str_replace_all(c("GIN" = "VODKA", "gin" = "vodka", "Gin" = "Vodka"))

Chris P  10:09 AM
```{r}
whole_text %>% 
  str_extract_all("(?i)(Department|Ministry|Ministrie|Mini[a-z]+)")
```

```{r}
whole_text %>%
  str_replace_all("Department", "Section") %>%
  str_replace_all("Ministry|Ministrie", "Department") %>%
  str_replace_all("Mini", "Dep") 
```

```{r}
pattern <- "[ ,\\.-][gG][iI][nN][ ,\\.-]"

whole_text %>%
  str_extract_all(pattern) %>%
  flatten_chr()
```


lists

```{r}
x <- 1:5

as.list(x)
```

```{r}

```

list[[1]]]

```{r}
named_list <- list(a = "I love R", b = 1:10)

```
```{r}
named_list$a

```

```{r}
student_info <- list(
                "Agnes" = list(height = 1.8, shoe_size = 8L),
                "Bobby" = list(height = 2.1, gender = "Male"),
                "Charlie" = list(gender = "Female", likes_beets = TRUE)
)
```

```{r}
student_info$Bobby$height

student_info[1]
```
Task - 5 minutes
Make a named list that contains a numeric vector and a character vector.
Access the second element of your list using double square brackets [[]]. What is it’s class?
Access the second element of your list using single square brackets []. What is it’s class?
Access the second element of your list by name. What is it’s class?

numcharlist <- list(numeric = c(21,45,70), character = ("Forever","Never","Sometimes")
```{r}
numcharlist = list(num = c(21, 45, 70), char = c("Forever", "Never", "Sometimes"))
```
```{r}

```
```{r}
m <- matrix(1:6, nrow = 2, ncol = 2, byrow = T)
```

m <- matrix(1:6, nrow = 2, ncol = 2, byrow = T)
```{r}
m[,1]
```
```{r}
m[2, c(2,3)]
```

```{r}
m -2
```
```{r}
rowSums(m)
```

```{r}
colSums(m)

```
```{r}
colMeans(m)
```
```{r}

  matrixd <- matrix(1:3, nrow = 3, ncol = 4)
```

```{r}
matrixd[2,3] 
```

```{r}
matrixd
```

#If Statements

if (weather == "sunny"){
    hang out washing
}

!=
>
<
<=
>=

```{r}
if (10 < 15){
  print("yes")
}
```

```{r}
if(5 %in% c(1,2,4,5)){
  print ("yes")
}
```

Write an if statement that prints 'Yes that divides by2' if a number x is divisible by 2. 
use %%2 == 0 as your expression), try it out for different values of x.

```{r} 
x=6
if(x %% 2 == 0){
  print ("Yes, that divides by 2")
}

```

```{r}
#more nonsense code
if (10 !=5){
  if (3 > 1){
    print("hello")
  }
}
```
Task - 10 minutes
Here’s an example of a nested if statement. Predict what the code is going to print out for the following combinations:

x is 10 and y is 3.

*Predicted output: "start of outer if block" 
[1] "Start of outer if block"
[1] "Inner if block 2"
[1] "End of outer if block"
[1] "After if statement"

x is 10 and y is 2.

*Predicted output: "start of outer if block"
[1] "Start of outer if block"
[1] "Inner if block 1"
[1] "Inner if block 2"
[1] "End of outer if block"
[1] "After if statement"

x is 2 and y is 10.

[1] "After if statement"

*Predicted output: "End of outer if block"

if (x > y) {
  print("Start of outer if block")

  if (x %% y == 0) {
    print("Inner if block 1")
  }

  if (y %in% c(1:5)) {
    print("Inner if block 2")
  }

  print("End of outer if block")
}

print("After if statement")


```{r}
x=2
y=10
if (x > y) {
  print("Start of outer if block")

  if (x %% y == 0) {
    print("Inner if block 1")
  }

  if (y %in% c(1:5)) {
    print("Inner if block 2")
  }

  print("End of outer if block")
}

print("After if statement")
```


#if-else

```{r}
if (4 < 5){
  print ("yes")
  else {
    print("no")
  }
}
```

Write an if statement that prints ‘Yes that divides by 2’ if a number x is divisible by 2 (hint: use %% 2 == 0 as your expression), try it out for different values of x.

```{r}
x = 1
if (x %% 2 == 0){
  print("Yes, that divides by 2")
  }else {print("No that does not divide")
  }

```

