---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
```

Review of Day 2 Lab work


Other peoples code

whole_text %>% 
  str_replace_all(c("GIN" = "VODKA", "gin" = "vodka", "Gin" = "Vodka"))

Chris P  10:09 AM
```{r}
whole_text %>% 
  str_extract_all("(?i)(Department|Ministry|Ministrie|Mini[a-z]+)")
```

```{r}
whole_text %>%
  str_replace_all("Department", "Section") %>%
  str_replace_all("Ministry|Ministrie", "Department") %>%
  str_replace_all("Mini", "Dep") 
```

```{r}
pattern <- "[ ,\\.-][gG][iI][nN][ ,\\.-]"

whole_text %>%
  str_extract_all(pattern) %>%
  flatten_chr()
```


lists

```{r}
x <- 1:5

as.list(x)
```

```{r}

```

list[[1]]]

```{r}
named_list <- list(a = "I love R", b = 1:10)

```
```{r}
named_list$a

```

```{r}
student_info <- list(
                "Agnes" = list(height = 1.8, shoe_size = 8L),
                "Bobby" = list(height = 2.1, gender = "Male"),
                "Charlie" = list(gender = "Female", likes_beets = TRUE)
)
```

```{r}
student_info$Bobby$height

student_info[1]
```
Task - 5 minutes
Make a named list that contains a numeric vector and a character vector.
Access the second element of your list using double square brackets [[]]. What is it’s class?
Access the second element of your list using single square brackets []. What is it’s class?
Access the second element of your list by name. What is it’s class?

numcharlist <- list(numeric = c(21,45,70), character = ("Forever","Never","Sometimes")
```{r}
numcharlist = list(num = c(21, 45, 70), char = c("Forever", "Never", "Sometimes"))
```
```{r}

```
```{r}
m <- matrix(1:6, nrow = 2, ncol = 2, byrow = T)
```

m <- matrix(1:6, nrow = 2, ncol = 2, byrow = T)
```{r}
m[,1]
```
```{r}
m[2, c(2,3)]
```

```{r}
m -2
```
```{r}
rowSums(m)
```

```{r}
colSums(m)

```
```{r}
colMeans(m)
```
```{r}

  matrixd <- matrix(1:3, nrow = 3, ncol = 4)
```

```{r}
matrixd[2,3] 
```

