---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
```

Review of Day 2 Lab work


Other peoples code

whole_text %>% 
  str_replace_all(c("GIN" = "VODKA", "gin" = "vodka", "Gin" = "Vodka"))

Chris P  10:09 AM
```{r}
whole_text %>% 
  str_extract_all("(?i)(Department|Ministry|Ministrie|Mini[a-z]+)")
```

```{r}
whole_text %>%
  str_replace_all("Department", "Section") %>%
  str_replace_all("Ministry|Ministrie", "Department") %>%
  str_replace_all("Mini", "Dep") 
```

```{r}
pattern <- "[ ,\\.-][gG][iI][nN][ ,\\.-]"

whole_text %>%
  str_extract_all(pattern) %>%
  flatten_chr()
```


lists

```{r}
x <- 1:5

as.list(x)
```

```{r}

```

list[[1]]]

```{r}
named_list <- list(a = "I love R", b = 1:10)

```
```{r}
named_list$a

```

```{r}
student_info <- list(
                "Agnes" = list(height = 1.8, shoe_size = 8L),
                "Bobby" = list(height = 2.1, gender = "Male"),
                "Charlie" = list(gender = "Female", likes_beets = TRUE)
)
```

```{r}
student_info$Bobby$height

student_info[1]
```
Task - 5 minutes
Make a named list that contains a numeric vector and a character vector.
Access the second element of your list using double square brackets [[]]. What is it’s class?
Access the second element of your list using single square brackets []. What is it’s class?
Access the second element of your list by name. What is it’s class?

numcharlist <- list(numeric = c(21,45,70), character = ("Forever","Never","Sometimes")
```{r}
numcharlist = list(num = c(21, 45, 70), char = c("Forever", "Never", "Sometimes"))
```
```{r}

```
```{r}
m <- matrix(1:6, nrow = 2, ncol = 2, byrow = T)
```

m <- matrix(1:6, nrow = 2, ncol = 2, byrow = T)
```{r}
m[,1]
```
```{r}
m[2, c(2,3)]
```

```{r}
m -2
```
```{r}
rowSums(m)
```

```{r}
colSums(m)

```
```{r}
colMeans(m)
```
```{r}

  matrixd <- matrix(1:3, nrow = 3, ncol = 4)
```

```{r}
matrixd[2,3] 
```

```{r}
matrixd
```

#If Statements

if (weather == "sunny"){
    hang out washing
}

!=
>
<
<=
>=

```{r}
if (10 < 15){
  print("yes")
}
```

```{r}
if(5 %in% c(1,2,4,5)){
  print ("yes")
}
```

Write an if statement that prints 'Yes that divides by2' if a number x is divisible by 2. 
use %%2 == 0 as your expression), try it out for different values of x.

```{r} 
x=6
if(x %% 2 == 0){
  print ("Yes, that divides by 2")
}

```

```{r}
#more nonsense code
if (10 !=5){
  if (3 > 1){
    print("hello")
  }
}
```
Task - 10 minutes
Here’s an example of a nested if statement. Predict what the code is going to print out for the following combinations:

x is 10 and y is 3.

*Predicted output: "start of outer if block" 
[1] "Start of outer if block"
[1] "Inner if block 2"
[1] "End of outer if block"
[1] "After if statement"

x is 10 and y is 2.

*Predicted output: "start of outer if block"
[1] "Start of outer if block"
[1] "Inner if block 1"
[1] "Inner if block 2"
[1] "End of outer if block"
[1] "After if statement"

x is 2 and y is 10.

[1] "After if statement"

*Predicted output: "End of outer if block"

if (x > y) {
  print("Start of outer if block")

  if (x %% y == 0) {
    print("Inner if block 1")
  }

  if (y %in% c(1:5)) {
    print("Inner if block 2")
  }

  print("End of outer if block")
}

print("After if statement")


```{r}
x=2
y=10
if (x > y) {
  print("Start of outer if block")

  if (x %% y == 0) {
    print("Inner if block 1")
  }

  if (y %in% c(1:5)) {
    print("Inner if block 2")
  }

  print("End of outer if block")
}

print("After if statement")
```


#if-else

```{r}
if (4 < 5){
  print ("yes")
  else {
    print("no")
  }
}
```

Write an if statement that prints ‘Yes that divides by 2’ if a number x is divisible by 2 (hint: use %% 2 == 0 as your expression), try it out for different values of x.

```{r}
x = 1
if (x %% 2 == 0){
  print("Yes, that divides by 2")
  }else {
    print("No that does not divide")
  }

```

x <- 5
y <- 10

Here’s an example of a nested if-else statement. Predict what it’s going to print out for the following conditions:.
When x is 5 and y is 10
When x is 6 and y is 12
When x is 6 and y is 13
```{r}
x <- 5
y <- 10

if (x %in% c(3, 4, 5)){
  print("x is in our list")
  
if (x == 5){
    print("x is exactly 5")
  }
} else {
  print("Start of else statement")
  if (y %% x == 0){
    print("x divides y")
  
  } else{
    print("x does not divide Y")
  }
  print ("End of else statement")
}
```
```{r}
for (sock in basket){
  peg it to the line
}
```


```{r}
weekdays <- c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday")

```
```{r}
for (day in weekdays) {
  phrase <- paste("The day is", day)
  print(phrase)
  }
```
```{r}

num = c(1:5)

for(number in num) {
  print(number)
}
print(1)
print(2)
print(3)
print(4)
print(5)
```
```{r}

current_value <- 1
end_point <- 10

while(current_value < end_point){
  current_value <- current_value + 1
  print(current_value)
}
```
```{r}

#another method
weekdays <- c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday")
length_weekday <- length(weekdays)

for (i in 1:length_weekday) {
  phrase <- paste("The day is", weekdays[i])
  print(phrase)
}
```
The [i] is essential.
It basically temporarily take the value of each element of the vector, one at a time, performs the contents of the loop, then take the value of the next element
i <- 1
```{r}
matrix <- matrix(1:3, 3, 4)
number_of_rows <- nrow(matrix)
number_of_cols <- ncol(matrix)

for (row_index in 1:number_of_rows) {
  for(col_index in 1:number_of_cols){
    print(matrix[row_index, col_index])
  }
}


```
Task - 10 mins
Run the code below to create an empty 5×5
5×5 matrix:
product_matrix <- matrix(nrow = 5, ncol = 5)
product_matrix
##      [,1] [,2] [,3] [,4] [,5]
## [1,]   NA   NA   NA   NA   NA
## [2,]   NA   NA   NA   NA   NA
## [3,]   NA   NA   NA   NA   NA
## [4,]   NA   NA   NA   NA   NA
## [5,]   NA   NA   NA   NA   NA
Check that the matrix is empty.
Now we’re going to fill product_matrix in the following way: each entry should be the product of the row index and position index at which the entry occurs. For example, the entry on the third row, fourth column, should be 3×4=12
3×4=12.
Get the matrix dimensions programatically (so that we could in the future apply this code to any size of matrix with minimal changes).
Hint: you can use the code above as a guide, although we won’t be printing out the matrix entries as we go. Instead, check your code by printing out the whole matrix at the end: just run the single statement product_matrix to do this.

```{r}
empty_matrix <- matrix(, nrow = 5, ncol = 5)

#define rows programatically
row_length <- nrow(empty_matrix)
col_length <- ncol(empty_matrix)
#start for loop
for (row_index in 1:row_length) { #for every row in the length of the matrix
  for (col_index in 1:col_length) { #for each column in that row
    product_matrix[row_index, col_index] <- row_index * col_index #index the cell value, and replace it with a new value
  }
}
product_matrix
```

Another example:

```{r}
example_matrix = matrix(1:25, nrow = 5, ncol = 5)
example_matrix
```
for (row_index in 1:5){
  for (col_index in 1:5){
    if (row_index == col_index){
      print(example_matrix[row_index, col_index])
    }
   }
}
output: 1,7,13,19,25

```{r}
for (row_index in 1:5){
  for (col_index in 1:5){
    if (row_index == col_index){
      print(example_matrix[row_index, col_index])
    }
   }
}
```

```{r}
# create your weekdays vector
weekdays <- c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday")
length_weekday <- length(weekdays)

for (i in 1:length_weekday) {
  phrase <- paste("It's", weekdays[i])
  print(phrase)}
  {
    else print ("last weekday!")
  }
```
for(day in weekdays){
  if (day == "Friday"){
    print(paste(day, "LAST WEEKDAY"))
  } else{
    print(day)
  }
}
```{r}
for(i in weekdays){
  if (i != "Friday"){
    print(i)
  } else{
    print("Last weekday!")
  }
}
```


Using (below code contains broken references and will not work as coded)
```{r}

my_data <- NULL

for (file in list.files("data")){
  part_data <- read_csv(file)
  my_data <- bind_rows(my_data, part_data)
}
```

```{r}
for (item in conflicted_list){
  
  if(item$has_address == TRUE) {
    address <- items$details$address
    addresses <- c(addresses, address)
  }
}
```

