---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
```

```{r}
nchar("hello", "chars", TRUE, NA)
```
```{r}
nchar(keepNA = NA, "chars", x = "hello", allowNA = TRUE)
```

```{r}
nchar("hello")
```

```{r}
paste("hello", "bye")
```

```{r}
nchar(c("hello", "bye", "yo"))
```
```{r}
function_name <- function(arg_1, arg_2, arg_3 = 5) {
  
  do something
  
  return(output)
}
  
```
```{r}
mult5x <- function(x) {
  return(x*5) #you don't need to use return, but it is best practices
  }
```
```{r}
mult5x(5)
```

```{r}
x=5
mult_by <- function(x, y=100) {
  return(x*y)
}
```



Task - 5 minutes
Write a function make_price() that takes as input any whole number, and returns it written as a price (i.e. with a ‘£’ in front of the number). For example 5 would become £5, and 123 would become £123. Try out your function a few times to test that it works.

```{r}
make_price <- function(x){
 x <- paste("£",x, sep = "")
  return(x)
}

make_price(5)
```

Write a function that takes as input a whoe number n, and returns the n-th triangle number.

nth_tri = function(n){
  (n*(n+1))%%2 -> x
  return(x)
}
```{r}
nth_tri = function(n){
  (n * (n + 1)) /2 -> x
  return(x)
}
```
```{r}
nth_tri(3)
```

Scope in programming
Suddenly we are using this term ‘scope’. What does it mean? Well, the ‘scope’ of a variable is basically all the places in our code that we can use that variable name without causing an error (the error being that R will complain that it can’t find the variable we are trying to use).
```{r}
multiply_by_3_add_2 <- function(x){
  
  times_3 <- x*3
  add_2 <- times_3 + 2
  
  return(add_2)
}
```

```{r}
add_3()
format_number()
```

```{r}
add_3 <- function(x){
  x + 3
}
```
```{r}
animals <- c("Cat", "Dog", "Monkey", "Elephant", "Frog")
hats <- c("Bowler", "Sun Hat", "Baseball Cap", "Fez")
trees <- c("Ash", "Elm", "Oak", "Willow", "Fir")

make_ordered <- function(my_vec){
  animals_sorted <- sort(my_vec)
  animals_joined <- str_c(animals_sorted, collapse = ', ')
  str_c("Ordered List:", animals_joined)

}

make_ordered(animals)
```

make function, index matrices



single vs. double square brackets

"[]" will always return the same class as the data structure you are indexing
"[[]]" used in reference to lists
