```{r}
library(tidyverse)
library(tsibbledata)
library(tsibble)
library(lubridate)
library(slider)
```
Try to periodically check in - am I answering what is being asked? Do I truly understand what I’m being asked? Do I understand how the answer to these questions/analysis will be implemented and affect the business? Do I know who the end user of my analysis is? It’s ok if not but be sure to ask (specific) questions to the client to find out.



```{r}
nyc_bikes_df <- nyc_bikes


glimpse(nyc_bikes_df)
index(nyc_bikes_df)
head(nyc_bikes)
tail(nyc_bikes)

#getting unique values for type, gender, subscriber

```
```{r}

distinct(nyc_bikes_df, type)
distinct(nyc_bikes_df, gender)
```


3 Task hints
You will probably want to use the data in column start_time to create date, month and year columns.
Summarising the data by aggregating hire counts by different measures of time (e.g. year, quarter, month, day) and then visualising the results is probably a good idea
When grouping time series data (tsibble), you need to use index_by instead of group_by

```{r}
#creating calendar and age columns
nyc_bikes_df %>% 
  mutate(start_date = ymd_hms(start_time),
         year = year(start_date),
         quarter = quarters(start_date),
         month = month(start_date),
         day = day(start_date),
         client_age = (year(start_date) - birth_year)
         )
```

